Fast algebraic filtering of surfaces from 3D medical images with Julia

### 2019-06-12 src/implementation.tex
posted Appendix

With $size=64$, the number of non-zeros within the sparse matrix $[\partial_{64^3}]$ is $\mathtt{nnz} = 4 792 266$, for a memory size of $9\times \mathtt{nnz}+8*262144 \simeq 45$ MB. The memory size of the sparse matrix is computed by considering $8+1$ bytes for non-zero element (which are exactly 6 per row), plus 8 bytes per each index of column start.

@@

\subsubsection{Code optimization}\label{sec:optimization}

>>>>

With $size=64$, the number of non-zeros within the sparse matrix $[\partial_{64^3}]$ is $\mathtt{nnz} = 4 792 266$, for a memory size of $9\times \mathtt{nnz}+8\times 262144 \simeq 45$ MB. The memory size of the sparse matrix is computed by considering $8+1$ bytes for non-zero element (which are exactly 6 per row), plus 8 bytes per each index of column start.

@@

### 2019-06-12 src/main.tex
working on algorithm design
filter design draft finished
splitted filter.tex file into design.tex and implementation.tex
some background materials
posted Appendix

\documentclass[11pt, oneside]{article}   	% use "amsart" instead of "article" for AMSLaTeX format
\usepackage{geometry}                		% See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   		% ... or a4paper or a5paper or ... 
%\geometry{landscape}                		% Activate for rotated page geometry
%\usepackage[parfill]{parskip}    		% Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}				% Use pdf, png, jpg, or eps§ with pdflatex; use eps in DVI mode
								% TeX will automatically convert eps --> pdf in pdflatex		
\usepackage{amssymb}

@@

@@

\include{intro}
\include{background}
\include{filter}
\include{examples}
\include{conclusion}

>>>>

\documentclass[11pt, oneside]{article}   	% use "amsart" instead of "article" for AMSLaTeX format
\usepackage{geometry}                		% See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   		% ... or a4paper or a5paper or ... 
%\geometry{landscape}                		% Activate for rotated page geometry
%\usepackage[parfill]{parskip}    		% Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}				% Use pdf, png, jpg, or eps§ with pdflatex; use eps in DVI mode
								% TeX will automatically convert eps --> pdf in pdflatex		
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{hyperref}

@@

\input{macros}

@@

\include{intro}
\include{background}
\include{design}
\include{implementation}
\include{examples}
\include{conclusion}

\appendix
\section{Appendix}
\subsection{Symbol list}

\begin{description}
\item[$\mathcal{I}$]  three-dimensional medical image
\\[-8mm]
\item[$\ell_1, \ell_2, \ell_3$]  dimensions of image
\\[-8mm]
\item[$\mathcal{S}$]  segment: subset of voxels
\\[-8mm]
\item[$\mathcal{B}$] 3D image block 
\\[-8mm]
\item[$size$] lateral dimension of cubic block $\mathcal{B}$ 
\\[-8mm]
\item[$n$]	number of blocks $\mathcal{B}$ (jobs) in $\mathcal{I}$
\\[-8mm]
\item[[$\partial_\mathcal{B}$] ]  boundary matrix for block $\mathcal{B}$
\\[-8mm]
\item[$C_p$] linear (vector) space of $p$-chains
\\[-8mm]
\item[$\nu\in C_p$] $p$-chain
\\[-8mm]
\item[[$\nu$]] coordinate representation (binary vector) of  $\nu$
\\[-8mm]
\item[$\E^3$] Euclidean 3-space
\end{description}

\subsection{Definitions}
\begin{description}
\item[CSC]  Compressed Sparse Column format for sparse matrices
\\[-8mm]
\item[Global coordinates]  Integer linear coordinates of $\mathcal{I}$
\\[-8mm]
\item[Local coordinates] Integer linear coordinates of $\mathcal{B}$
\\[-8mm]
\item[Cartesian coordinates] Integer triples $(i,j,k)$ one-to-one with voxels 
\\[-8mm]
\item[Voxels] individual elements in 3D image (3-cells)
\\[-8mm]
\item[$p$-chain] formal linear combination of $p$-cells with coefficients in $\{0,1\}$
\\[-8mm]
\item[Coord. repr.]  binary vector (for $p$-chains) or binary matrix (for chain operators)
\\[-8mm]
\item[Quad]	geometric quadrilateral; convex polygon with four vertices 
\\[-8mm]
\item[Foreground voxel] individual element of a segment $\mathcal{S}$
\\[-8mm]
\item[Segment]	subset of voxels resulting from image segmentation
\end{description}
